Exploratory analysis page
========================================================

Library and load data
---
```{r}
library(survey)
library(ProjectTemplate)
setwd('~/Dropbox/Mike/NSCH_11_12/')
rm(list = ls())
load.project()
```

Specify survey design
---
```{r}
nsch.design <- svydesign(id=~IDNUMR, strata = ~STATE + SAMPLE, data = data, weights = ~NSCHWT)
nsch.design
```

Sex
----
```{r}
summary(data$sex_11)
prop.table(table(data$sex_11))
svymean(~sex_11, nsch.design, na.rm = T)
svytotal(~sex_11, nsch.design, na.rm = T)
```

Age
----

Race
------

Ethnicity
----

Poverty
-----

PEDS variables
----
```{r}
summary(data$peds)
svymean(~peds, nsch.design, na.rm = T)
svytotal(~peds, nsch.design, na.rm = T)
```

Flourishing items 0-5
----
```{r}
summary(data[469:472])
summary(data$ind2_3_11)

svymean(~ind2_3_11, nsch.design, na.rm = T)
svytotal(~ind2_3_11, nsch.design, na.rm = T)
```


Flourishing items 6-17 yo
----
```{r}
summary(data[475:477])
summary(data$ind2_4_11)

svymean(~ind2_4_11, nsch.design, na.rm = T)
svytotal(~ind2_4_11, nsch.design, na.rm = T)
```

Chronic health or developmental conditions and severity
----
```{r}
for(i in 414:420) {
  print(names(data)[i])
  print(svymean(data[i], na.rm = T, design = nsch.design))
  print(svymean(data[i + 20], na.rm = T, design = nsch.design))
  }
for(i in 421:422) {
  print(names(data)[i])
  print(svymean(data[i], na.rm = T, design = nsch.design))
  print(svymean(data[i + 29], na.rm = T, design = nsch.design))
}
for(i in 423:431) {
  print(names(data)[i])
  print(svymean(data[i], na.rm = T, design = nsch.design))
  print(svymean(data[i + 18], na.rm = T, design = nsch.design))
}
svymean(data[432], design = nsch.design, na.rm = T)
```

Medical Home
----
```{r}
svymean(~pdn_11, nsch.design, na.rm = T)
svymean(~famcent_11, nsch.design, na.rm = T)
svymean(~norefprb_11, nsch.design, na.rm = T)
svymean(~usual_11, nsch.design, na.rm = T)
svymean(~carecoor_11, nsch.design, na.rm = T)
svymean(~mh_comp, nsch.design, na.rm = T)
```

Dental care
----
One hypothesis might be that kids with ADHD and autism (or any special health care need) see dentists less often. There are several dental variables including preventive care, unmet need, and any dental care.  

```{r}
for(i in 133:135) {
  dentalnames <- c("Saw dentist for any reason in past 12 mos", "Number of preventive dental visits in past 12 mos", "Had a toothache, decayed teeth or unfilled cavity in past 12 mos")
  print(dentalnames[i-132])
  print(svymean(data[i], nsch.design, na.rm = T))
}
```

Delayed or not received dental visits
```{r}
svymean(~K4Q28X02, nsch.design, na.rm = T)
```

Services received for developmental needs
------
### Receipt of services  
Child received EI/OT/ST/Behavior Tx services for developmental issues. We also need to figure out whether the child actually was eligible for these issues (using PEDS?)
```{r}
str(data$K4Q36)
levels(data$K4Q36)
summary(data$K4Q36)
```

### Age of services started  
It looks like age was asked by month until the child was 2 years old. I'll need to recode the year kids into months. Done in munge script 01-A.R.
```{r}
str(data$K4Q37)
levels(data$K4Q37)
summary(data$K4Q37)

str(data$K4Q37_A)
levels(data$K4Q37_A)
```
