Exploratory analysis page
========================================================

Library and load data
---
```{r}
library(survey)
library(ProjectTemplate)
setwd('~/Dropbox/Mike/NSCH_11_12/')
rm(list = ls())
load.project()
```

Specify survey design
---
```{r}
nsch.design <- svydesign(id=~IDNUMR, strata = ~STATE + SAMPLE, data = data, weights = ~NSCHWT)
nsch.design
```

Sex
----
```{r}
summary(data$sex_11)
prop.table(table(data$sex_11))
svymean(~sex_11, nsch.design, na.rm = T)
svytotal(~sex_11, nsch.design, na.rm = T)
```

Age
----
Age is not provided in month intervals, only in years. This makes it more difficult to interpret the youngest age children, but we can create some 6 month interval categories for children under 2 with the data available. I did this in the munge file.
```{r}
summary(data$AGEYR_CHILD)
svytable(~AGEYR_CHILD, nsch.design)
plot(svytable(~AGEYR_CHILD, nsch.design))
```

Toddler age groups are 0-5, 6-11, 12-17 and 18-23 months.

```{r}
summary(data$toddler.age)
svytable(~toddler.age, nsch.design)
```

Race
------
Race is classified differently across all states and in Hawaii.
```{r}
summary(data$RACER)
svytotal(~RACER, nsch.design, na.rm = T)
svytotal(~RACE_HI, nsch.design, na.rm = T)
```

Ethnicity
----
```{r}
summary(data$HISPANIC)
svytotal(~HISPANIC, nsch.design, na.rm = T)
svytable(~HISPANIC + RACER, nsch.design)
```

Poverty
-----
```{r}
summary(data$povlev4_11)
svytotal(~povlev4_11, nsch.design)
```

Maternal education level
-----
```{r}
summary(data$EDUC_MOMR)
svytable(~EDUC_MOMR, design = nsch.design)
```


Birthweight
----
```{r}
str(data$K2Q04R)
summary(data$K2Q04R)
# needs to be changed into grams for easier interpretation
# done in munge file 01-A.R
svymean(~BWgrams, nsch.design, na.rm = T)
svyquantile(~BWgrams, nsch.design, seq(0, 1, by = 0.25), na.rm = T)
svyhist(~BWgrams, nsch.design, xlab = "Birthweight (g)", ylab = "Frequency", main = "NSCH 2011-2012 Birthweight")
```


PEDS variables
----
```{r}
summary(data$peds)
svymean(~peds, nsch.design, na.rm = T)
svytotal(~peds, nsch.design, na.rm = T)
```

Flourishing items 0-5
----
```{r}
summary(data[469:472])
summary(data$ind2_3_11)

svymean(~ind2_3_11, nsch.design, na.rm = T)
svytotal(~ind2_3_11, nsch.design, na.rm = T)
```


Flourishing items 6-17 yo
----
```{r}
summary(data[475:477])
summary(data$ind2_4_11)

svymean(~ind2_4_11, nsch.design, na.rm = T)
svytotal(~ind2_4_11, nsch.design, na.rm = T)
```

Chronic health or developmental conditions and severity
----
```{r}
for(i in 414:420) {
  print(names(data)[i])
  print(svymean(data[i], na.rm = T, design = nsch.design))
  print(svymean(data[i + 20], na.rm = T, design = nsch.design))
  }
for(i in 421:422) {
  print(names(data)[i])
  print(svymean(data[i], na.rm = T, design = nsch.design))
  print(svymean(data[i + 29], na.rm = T, design = nsch.design))
}
for(i in 423:431) {
  print(names(data)[i])
  print(svymean(data[i], na.rm = T, design = nsch.design))
  print(svymean(data[i + 18], na.rm = T, design = nsch.design))
}
svymean(data[432], design = nsch.design, na.rm = T)
```

Medical Home
----
```{r}
svymean(~pdn_11, nsch.design, na.rm = T)
svymean(~famcent_11, nsch.design, na.rm = T)
svymean(~norefprb_11, nsch.design, na.rm = T)
svymean(~usual_11, nsch.design, na.rm = T)
svymean(~carecoor_11, nsch.design, na.rm = T)
svymean(~mh_comp, nsch.design, na.rm = T)
```

Dental care
----
One hypothesis might be that kids with ADHD and autism (or any special health care need) see dentists less often. There are several dental variables including preventive care, unmet need, and any dental care.  

```{r}
for(i in 133:135) {
  dentalnames <- c("Saw dentist for any reason in past 12 mos", "Number of preventive dental visits in past 12 mos", "Had a toothache, decayed teeth or unfilled cavity in past 12 mos")
  print(dentalnames[i-132])
  print(svymean(data[i], nsch.design, na.rm = T))
}
```

Delayed or not received dental visits
```{r}
svymean(~K4Q28X02, nsch.design, na.rm = T)
```

Services received for developmental needs
------
### Receipt of services  
Child received EI/OT/ST/Behavior Tx services for developmental issues. We also need to figure out whether the child actually was eligible for these issues (using PEDS?)
```{r}
str(data$K4Q36)
levels(data$K4Q36)
summary(data$K4Q36)
```

### Age of services started  
It looks like age was asked by month until the child was 2 years old. I'll need to recode the year kids into months. Done in munge script 01-A.R.
```{r}
str(data$K4Q37)
levels(data$K4Q37)
summary(data$K4Q37)

str(data$K4Q37_A)
levels(data$K4Q37_A)
```

# Age of autism or developmental delay diagnosis
```{r}


summary(data$K2Q35A_2)
str(data$K2Q35A_2)

```

Indicator 1.1: In general how would you describe [child name]'s health?
----
I am using this indicator to test the survey design statement. If it works properly, we should have the same result as given on http://childhealthdata.org/browse/survey/results?q=2456&r=1

```{r}
summary(data$ind1_1_11)
svytotal(~ind1_1_11, nsch.design, na.rm = T)
overall.health <- svymean(~ind1_1_11, nsch.design, na.rm = T)
overall.health
confint(overall.health)
```
### Success! The result is the same!